### 2013-07-15 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding nonlinear comparison data to document

%%---------------------------------------------------------------------------%%
\section{Navier-Stokes Benchmark Problems\ }
\label{sec:ns_benchmarks}
To verify the FANM method for nonlinear problems, we choose benchmark
solutions for the 2-dimensional, steady, incompressible Navier-Stokes
equations on a rectilinear grid in much the same way as Shadid and
Pawlowski's work on Newton-Krylov methods for the solution of these
equations \citep{shadid_inexact_1997,pawlowski_globalization_2006}. We
define these equations as follows:
\begin{subequations}
  \begin{gather}
    \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
    \ve{g} = \ve{0}
    \label{eq:ns_momentum}\\
    \nabla \cdot \ve{u} = 0
    \label{eq:ns_continuity}\\
    \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0\:,
    \label{eq:ns_energy}
  \end{gather}
  \label{eq:navier_stokes}
\end{subequations}
where $\rho$ is the fluid density, $\ve{u}$ is the fluid velocity,
$C_p$ the specific heat capacity at constant pressure of the fluid,
$T$ the temperature of the fluid, and $\ve{g}$ the acceleration due to
gravity. Eq~(\ref{eq:ns_momentum}) provides momentum transport,
Eq~(\ref{eq:ns_continuity}) provides the mass balance, and
Eq~(\ref{eq:ns_energy}) provides energy transport with viscous
dissipation effects neglected. In addition, we close the system with
the following equations:
\begin{subequations}
  \begin{gather}
    \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
    \label{eq:ns_stress_tensor}\\
    \ve{q} = - k \nabla T\:,
    \label{eq:ns_heat_flux}
  \end{gather}
  \label{eq:ns_closure}
\end{subequations}
where $\ve{T}$ is the stress tensor, $P$ is the hydrodynamic pressure,
$\mu$ is the dynamic viscosity of the fluid, $\ve{q}$ is the heat flux
in the fluid, and $k$ is the thermal conductivity of the fluid. This
set of strongly coupled equations possesses both the nonlinearities
and asymmetries that we are seeking for qualification of the FANM
method. Further, physical parameters within these equations can be
tuned to enhance the nonlinearities. We will then apply these
equations to the following three standard benchmark problems.

@@

Temperature solutions for these equations are given in
Figure~\ref{fig:convection_isotherms} for Rayleigh numbers of
\sn{1}{3}, \sn{1}{4}, \sn{1}{5} and \sn{1}{6}. Note that as the
Rayleigh number is increased, the fluid begins to rotate in the
clockwise direction. This causes the temperature gradients to rotate
as well with the fluid, given the increased rotation observed for the
isotherms in the figure.

@@

\subsection{Backward-Facing Step Problem}
\label{subsec:backward_facing_step}
The third benchmark was generated by Gartling in 1990 and consists of
both flow over a backward step and an outflow boundary condition
\citep{gartling_test_1990}. Using the mass and momentum equations
while neglecting the energy equation, this problem utilizes a longer
domain with a 1/30 aspect ratio with the boundary conditions as shown
in Figure~\ref{fig:backward_facing_step}.
\begin{figure}[t!]
  \begin{center}
    \scalebox{1.3}{
      \input{chapters/nonlinear_problem/backward_facing_step.pdftex_t} }
  \end{center}
  \caption{\textbf{Problem setup for the backward facing step
      benchmark.} \textit{Zero velocity boundary conditions are
      applied at the top and bottom of the domain while the outflow
      boundary condition on the right boundary is represented by zero
      stress tensor components in the direction of the flow. For the
      inlet conditions, the left boundary is split such that the top
      half has a fully formed parabolic flow profile and the bottom
      half has a zero velocity condition, simulating flow over a
      step.}}
  \label{fig:backward_facing_step}
\end{figure}
In this problem, the inflow condition is specified by a fully-formed
parabolic flow profile over a zero velocity boundary representing a
step. The flow over this step will generate a recirculating back-flow
under the inlet flow towards the step. As in the lid driven cavity
problem, the nonlinear behavior of this benchmark and the difficulty
in obtaining a solution is dictated by the Reynolds number of the
fluid. In Shadid's work, a $20 \times 400$ non-square rectilinear grid
was used to discretize the domain with Reynolds number up to
\sn{8}{2}.

@@

@@

@@

@@

@@

@@

>>>>

%%---------------------------------------------------------------------------%%
\section{Navier-Stokes Benchmark Problems\ }
\label{sec:ns_benchmarks}
To verify the FANM method for nonlinear problems, we choose benchmark
solutions for the 2-dimensional, steady, incompressible Navier-Stokes
equations on a rectilinear grid in much the same way as Shadid and
Pawlowski's work on Newton-Krylov methods for the solution of these
equations \citep{shadid_inexact_1997,pawlowski_globalization_2006}. We
define these equations as follows:
\begin{subequations}
  \begin{gather}
    \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
    \ve{g} = \ve{0}
    \label{eq:ns_momentum}\\
    \nabla \cdot \ve{u} = 0
    \label{eq:ns_continuity}\\
    \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0\:,
    \label{eq:ns_energy}
  \end{gather}
  \label{eq:navier_stokes}
\end{subequations}
where $\rho$ is the fluid density, $\ve{u}$ is the fluid velocity,
$C_p$ the specific heat capacity at constant pressure of the fluid,
$T$ the temperature of the fluid, and $\ve{g}$ the acceleration due to
gravity. Eq~(\ref{eq:ns_momentum}) provides momentum transport,
Eq~(\ref{eq:ns_continuity}) provides the mass balance, and
Eq~(\ref{eq:ns_energy}) provides energy transport with viscous
dissipation effects neglected. In addition, we close the system with
the following equations:
\begin{subequations}
  \begin{gather}
    \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
    \label{eq:ns_stress_tensor}\\
    \ve{q} = - k \nabla T\:,
    \label{eq:ns_heat_flux}
  \end{gather}
  \label{eq:ns_closure}
\end{subequations}
where $\ve{T}$ is the stress tensor, $P$ is the hydrodynamic pressure,
$\mu$ is the dynamic viscosity of the fluid, $\ve{q}$ is the heat flux
in the fluid, and $k$ is the thermal conductivity of the fluid. This
set of strongly coupled equations possesses both the nonlinearities
and asymmetries that we are seeking for qualification of the FANM
method. Further, physical parameters within these equations can be
tuned to enhance the nonlinearities. We will then apply these
equations to the following two standard benchmark problems.

@@

Temperature solutions for these equations are given in
Figure~\ref{fig:convection_isotherms} for Rayleigh numbers of
\sn{1}{3}, \sn{1}{4}, \sn{1}{5} and \sn{1}{6}. Note that as the
Rayleigh number is increased, the fluid begins to rotate in the
clockwise direction. This causes the temperature gradients to rotate
as well with the fluid, given the increased rotation observed for the
isotherms in the figure. As the Rayleigh number increases, thermal
energy and momentum transport in the system become more dominated by
convection rather than diffusion, causing the nonlinearities in the
advective derivatives to grow.

@@

@@

As with the radiation transport calculations in the previous chapter,
algrebraic preconditioning with the multigrid method results in dense
linear systems. To mitigate this, the reduced domain approximation was
again applied to the Monte Carlo solution within the MCSA solve
occuring at each nonlinear iteration. The values used for the
approximation will be given for each benchmark problem.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 10404 & - \\
      Initial Temperature & 0.0 & $K$ \\
      Density & 1.0 & $kg / m^3$ \\
      Specific Heat & 1.0 & J / $(kg \times K)$ \\
      Dynamic Viscosity & 0.71 & $N \times s / m^2$ \\
      Thermal Conductivity & 1.0 & $W / (m \times K)$ \\
      Thermal Expansion Coefficient & 1000 & $1 / K$ \\
      Thermal Diffusivity & 1.0 & $m^2 / s$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Gravitational Acceleration & 10 & $m / s^2$ \\
      Cavity Characteristic Length & 1.0 & $m$ \\
      Prandtl Number & 0.71 & - \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Rayleigh number
      is varied by modifying the hot boundary temperature to induce
      larger temperature gradients and bouyancy-driven flow.}}
  \label{tab:thermal_convection_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Histories & 500,000 per iteration \\
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      Reduced Domain Fill Level & 200 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification MCSA
      solver parameters.} \textit{No relaxation parameters or variance
      reduction techniques were used with MCSA other than the reduced
      domain approximation.}}
  \label{tab:convection_mcsa_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -1.288835730E-05 & -1.288835730E-05 \\
      Minimum $U_x$ & -3.677243960E+00 & -3.677243960E+00 \\
      Maximum $U_x$ & 3.688908550E+00 & 3.688908550E+00 \\
      \hline
      Average $U_y$ & 3.403670530E-02 & 3.403670530E-02 \\
      Minimum $U_y$ & -3.721178580E+00 & -3.721178580E+00 \\
      Maximum $U_y$ & 3.791483420E+00 & 3.791483420E+00 \\
      \hline
      Average $P$ & 2.345554770E+02 & 2.345554770E+02 \\
      Minimum $P$ & -5.509779180E+00 & -5.509779180E+00 \\
      Maximum $P$ & 4.994885560E+02 & 4.994885560E+02 \\
      \hline
      Average $T$ & 3.595148700E-02 & 3.595148700E-02 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{3}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e3_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -7.489201240E-04 & -7.489201240E-04 \\
      Minimum $U_x$ & -1.607318000E+01 & -1.607318000E+01 \\
      Maximum $U_x$ & 1.669098270E+01 & 1.669098270E+01 \\
      \hline
      Average $U_y$ & 3.377624420E-01 & 3.377624420E-01 \\
      Minimum $U_y$ & -1.932174800E+01 & -1.932174800E+01 \\
      Maximum $U_y$ & 2.047326820E+01 & 2.047326820E+01 \\
      \hline
      Average $P$ & 1.861894950E+03 & 1.861894950E+03 \\
      Minimum $P$ & -3.353416240E+01 & -3.353416240E+01 \\
      Maximum $P$ & 4.440642810E+03 & 4.440642810E+03 \\
      \hline
      Average $T$ & 3.510568440E-01 & 3.510568440E-01 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{4}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e4_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -2.043639370E-02 & -2.043639370E-02 \\
      Minimum $U_x$ & -3.814922470E+01 & -3.814922470E+01 \\
      Maximum $U_x$ & -3.814922470E+01 & -3.814922470E+01 \\
      \hline
      Average $U_y$ & 2.774864300E+00 & 2.774864300E+00 \\
      Minimum $U_y$ & -6.038682990E+01 & -6.038682990E+01 \\
      Maximum $U_y$ & 7.873873560E+01 & 7.873873560E+01 \\
      \hline
      Average $P$ & 1.324208380E+04 & 1.324208380E+04 \\
      Minimum $P$ & -1.390235490E+02 & -1.390235490E+02 \\
      Maximum $P$ & 3.559215530E+04 & 3.559215530E+04 \\
      \hline
      Average $T$ & 3.027827770E+00 & 3.027827770E+00 \\
      Minimum $T$ & 1.626405740E-02 & 1.626405740E-02 \\
      Maximum $T$ & 7.162571130E+00 & 7.162571130E+00 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{5}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e5_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -1.802569840E-01 & -1.802569840E-01 \\
      Minimum $U_x$ & -6.292084130E+01 & -6.292084130E+01 \\
      Maximum $U_x$ & 2.951113240E+02 & 2.951113240E+02 \\
      \hline
      Average $U_y$ & 1.336398550E+01 & 1.336398550E+01 \\
      Minimum $U_y$ & -1.345663290E+02 & -1.345663290E+02 \\
      Maximum $U_y$ & 3.227873890E+02 & 3.227873890E+02 \\
      \hline
      Average $P$ & 6.354313840E+04 & 6.354313840E+04 \\
      Minimum $P$ & -1.356309630E+02 & -1.356309630E+02 \\
      Maximum $P$ & 2.316308730E+05 & 2.316308730E+05 \\
      \hline
      Average $T$ & 1.780727610E+01 & 1.780727610E+01 \\
      Minimum $T$ & 8.265788890E-02 & 8.265788890E-02 \\
      Maximum $T$ & 7.098873170E+01 & 7.098873170E+01 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{6}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e6_results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 7803 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 0.71 & $N \times s / m^2$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Gravitational Acceleration & 10 & $m / s^2$ \\
      Cavity Characteristic Length & 1.0 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow driven by inertial forces.}}
  \label{tab:lid_driven_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      Histories, Re=100 & 500,000 per iteration \\
      Histories, Re=300 & 500,000 per iteration \\
      Histories, Re=500 & 500,000 per iteration \\
      Histories, Re=700 & 1,000,000 per iteration \\
      Reduced Domain Fill Level, Re=100 & 200 \\
      Reduced Domain Fill Level, Re=300 & 200 \\
      Reduced Domain Fill Level, Re=500 & 200 \\
      Reduced Domain Fill Level, Re=700 & 300 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification MCSA solver
      parameters.} \textit{No relaxation parameters or variance
      reduction techniques were used with MCSA other than the reduced
      domain approximation. Different values of fill level for the
      reduced domain approximation and histories per iteration were
      used at different Reynolds numbers due to convergence
      requirements.}}
  \label{tab:driven_mcsa_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 1.165632320E-01 & 1.165632320E-01 \\
      Minimum $U_x$ & -2.423642920E+01 & -2.423642920E+01 \\
      Maximum $U_x$ & 9.742670880E+01 & 9.742670880E+01 \\
      \hline
      Average $U_y$ & 2.038480420E-02 & 2.038480420E-02 \\
      Minimum $U_y$ & -5.266315430E+01 & -5.266315430E+01 \\
      Maximum $U_y$ & 2.720044160E+01 & 2.720044160E+01 \\
      \hline
      Average $P$ & -1.656193900E+02 & -1.656193900E+02 \\
      Minimum $P$ & -9.635479370E+03 & -9.635479370E+03 \\
      Maximum $P$ & 1.854517020E+04 & 1.854517020E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 100.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re100_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 3.382078040E-01 & 3.382078040E-01 \\
      Minimum $U_x$ & -9.467140360E+01 & -9.467140360E+01 \\
      Maximum $U_x$ & 2.895885380E+02 & 2.895885380E+02 \\
      \hline
      Average $U_y$ & 8.780242440E-02 & 8.780242440E-02 \\
      Minimum $U_y$ & -1.830156060E+02 & -1.830156060E+02 \\
      Maximum $U_y$ & 8.827373340E+01 & 8.827373340E+01 \\
      \hline
      Average $P$ & -2.830380160E+03 & -2.830380160E+03 \\
      Minimum $P$ & -2.352177540E+04 & -2.352177540E+04 \\
      Maximum $P$ & 9.254997120E+04 & 9.254997120E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 300.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 5.098921320E-01 & 5.098921320E-01 \\
      Minimum $U_x$ & -1.731861690E+02 & -1.731861690E+02 \\
      Maximum $U_x$ & 4.789146040E+02 & 4.789146040E+02 \\
      \hline
      Average $U_y$ & 1.365493140E-01 & 1.365493140E-01 \\
      Minimum $U_y$ & -3.170930360E+02 & -3.170930360E+02 \\
      Maximum $U_y$ & 1.655401440E+02 & 1.655401440E+02 \\
      \hline
      Average $P$ & -9.378317550E+03 & -9.378317550E+03 \\
      Minimum $P$ & -4.155215280E+04 & -4.155215280E+04 \\
      Maximum $P$ & 2.058742010E+05 & 2.058742010E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a
      Reynolds number of 500.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:driven_re500_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 6.479541170E-01 & 6.479541170E-01 \\
      Minimum $U_x$ & -2.550685400E+02 & -2.550685400E+02 \\
      Maximum $U_x$ & 6.663054900E+02 & 6.663054900E+02 \\
      \hline
      Average $U_y$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $U_y$ & -4.491052980E+02 & -4.491052980E+02 \\
      Maximum $U_y$ & 2.474376340E+02 & 2.474376340E+02 \\
      \hline
      Average $P$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $P$ & -6.241704500E+04 & -6.241704500E+04 \\
      Maximum $P$ & 3.518174810E+05 & 3.518174810E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 700.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re700_results}
\end{table}

@@

Using the benchmarks from the verification, we now compare the
performance of the FANM method against a conventional Krylov
method. For each benchmark, we will analyze the iterative performance
of both the Newton solver and the linear solver used to compute the
correction vector at each step. In addition, timing results will be discussed

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      \sn{1}{3} & 5 & 5 \\
      \sn{1}{4} & 7 & 7 \\
      \sn{1}{5} & 9 & 10 \\
      \sn{1}{6} & 11 & 11 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_nonlinear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{GMRES Iterations}&
      \multicolumn{1}{c}{MCSA Iterations}\\
      \hline
      \sn{1}{3} & 23 & 18 \\
      \sn{1}{4} & 23 & 17 \\
      \sn{1}{5} & 25 & 20 \\
      \sn{1}{6} & 39 & 25 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity total sum of linear
      iterations for all nonlinear iterations.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_linear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      \sn{1}{3} & \sn{4.542}{-14} & \sn{1.208}{-14} \\
      \sn{1}{4} & \sn{1.045}{-12} & \sn{7.012}{-13} \\
      \sn{1}{5} & \sn{1.784}{-12} & \sn{1.059}{-12} \\
      \sn{1}{6} & \sn{3.404}{-12} & \sn{3.479}{-12} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:convection_residual_norm_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      \sn{1}{3} & 338 \\
      \sn{1}{4} & 336 \\
      \sn{1}{5} & 346 \\
      \sn{1}{6} & 465 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:convection_speedup_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      100 & 6 & 6 \\
      300 & 9 & 9 \\
      500 & 11 & 11 \\
      700 & 14 & 10 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:driven_nonlinear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{GMRES Iterations}&
      \multicolumn{1}{c}{MCSA Iterations}\\
      \hline
      100 & 27 & 42 \\
      300 & 35 & 52 \\
      500 & 41 & 56 \\
      700 & 21 & 14 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity total sum of linear
      iterations for all nonlinear iterations.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:driven_linear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      100 & \sn{5.453}{-14} & \sn{6.577}{-14} \\
      300 & \sn{2.537}{-13} & \sn{2.779}{-13} \\
      500 & \sn{6.367}{-13} & \sn{6.252}{-13} \\
      700 & \sn{9.159}{-13} & \sn{1.282}{-12} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:driven_residual_norm_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      100 & 299 \\
      300 & 322 \\
      500 & 288 \\
      700 & 488 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:driven_speedup_comparison}
\end{table}

### 2013-07-15 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding nonlinear comparison data to document

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Histories & 1 per DOF \\
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point & Richardson \\
      Estimator & Collision \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parallel MCSA verification solver parameters.}}
  \label{tab:parallel_mcsa_parameters}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Histories & 1 per DOF \\
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parallel MCSA verification solver parameters.}
    \textit{No relaxation parameters or variance reduction techniques
      were used with MCSA.}}
  \label{tab:parallel_mcsa_parameters}
\end{table}
